### 2025-05-15 manuscript/supplement.Rmd
change manuscript format to Fisheries Research
Make some fig pages landscape and adjust

@@

```{r nsamps-plot, echo=FALSE, fig.align='center', fig.height=5, fig.width=8, fig.cap = nsamps_plot_fig_caption, message=FALSE, warning=FALSE}
nsamps_plot
```

@@

```{r ss-hsp-plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, fig.cap = ss_hsp_plot_fig_caption, message=FALSE, warning=FALSE}
ckmr_hsp_plot
```

@@

```{r parnll-plot, echo=FALSE, fig.align='center', fig.height=8, fig.width=10, fig.cap = parnll_plot_fig_caption, message=FALSE, warning=FALSE}
para_res_plot_nll 
```

```{r par-plot, echo=FALSE, fig.align='center', fig.height=8, fig.width=10, fig.cap = par_plot_fig_caption, message=FALSE, warning=FALSE}
para_res_plot 
```

```{r cor-plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, fig.cap = cor_plot_fig_caption, message=FALSE, warning=FALSE}
cor_plot 
```

```{r fac-plot, echo=FALSE, fig.align='center', fig.height=9, fig.width=9, fig.cap = fac_plot_fig_caption, message=FALSE, warning=FALSE}
f_ac_plot 
```

```{r mac-plot, echo=FALSE, fig.align='center', fig.height=9, fig.width=9, fig.cap = mac_plot_fig_caption, message=FALSE, warning=FALSE}
m_ac_plot 
```

```{r fpr-plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, fig.cap = fpr_plot_fig_caption, message=FALSE, warning=FALSE, out.extra='angle=90', out.width = "8in", out.height="10in"}
fpr_plot
```

```{r mpr-plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, fig.cap = mpr_plot_fig_caption, message=FALSE, warning=FALSE, out.extra='angle=90', out.width = "8in", out.height="10in"}
mpr_plot
```

>>>>

  - \usepackage{pdflscape}

@@

\newpage
\begin{landscape}
```{r nsamps-plot, echo=FALSE, fig.align='center', fig.height=5, fig.width=8, fig.cap = nsamps_plot_fig_caption, message=FALSE, warning=FALSE}
nsamps_plot
```

\newpage

@@

\newpage

```{r ss-hsp-plot, echo=FALSE, fig.align='center', fig.height=6, fig.width=8.5, fig.cap = ss_hsp_plot_fig_caption, message=FALSE, warning=FALSE}
ckmr_hsp_plot
```

\newpage

@@

\newpage

```{r parnll-plot, echo=FALSE, fig.align='center', fig.height=6.5, fig.width=8, fig.cap = parnll_plot_fig_caption, message=FALSE, warning=FALSE}
para_res_plot_nll 
```

\newpage

```{r par-plot, echo=FALSE, fig.align='center', fig.height=6.5, fig.width=8, fig.cap = par_plot_fig_caption, message=FALSE, warning=FALSE}
para_res_plot 
```

\newpage

```{r cor-plot, echo=FALSE, fig.align='center', fig.height=6.5, fig.width=8, fig.cap = cor_plot_fig_caption, message=FALSE, warning=FALSE}
cor_plot 
```

\newpage

```{r fac-plot, echo=FALSE, fig.align='center', fig.height=6, fig.width=7.5, fig.cap = fac_plot_fig_caption, message=FALSE, warning=FALSE}
f_ac_plot 
```

\newpage

```{r mac-plot, echo=FALSE, fig.align='center', fig.height=6, fig.width=7.5, fig.cap = mac_plot_fig_caption, message=FALSE, warning=FALSE}
m_ac_plot 
```

\newpage

```{r fpr-plot, echo=FALSE, fig.align='center', fig.height=7.5, fig.width=10, fig.cap = fpr_plot_fig_caption, message=FALSE, warning=FALSE, out.width = "8.5in", out.height="6.375in"}
fpr_plot
```

\newpage

```{r mpr-plot, echo=FALSE, fig.align='center', fig.height=7.5, fig.width=10, fig.cap = mpr_plot_fig_caption, message=FALSE, warning=FALSE, out.width = "8.5in", out.height="6.375in"}
mpr_plot
```
\end{landscape}
